Papers

### 2024-05-12 done.qmd
update

Recording things i've done which don't go under [Publications](https://tomstafford.sites.sheffield.ac.uk/outputs/scholarly-publications), 
[Talks](https://tomstafford.sites.sheffield.ac.uk/outputs/talks) or Newsletter: <https://tomstafford.substack.com/>. Most of these posted to [Mastodon](https://mastodon.online/@tomstafford) too.

@@

@@

@@

>>>>

Recording things i've done which don't go under  [Papers](papers.html), 
[Talks](https://tomstafford.sites.sheffield.ac.uk/outputs/talks) or Newsletter: <https://tomstafford.substack.com/>. For current preoccupations, see [here](news.html).

@@

# 2021

2021: [The Experiment Design Checklist](https://tomstafford.github.io/psy-checklist/)

@@

2020: [The Letters of Pope Gregory VII - pilot project](https://figshare.com/articles/dataset/The_Letters_of_Pope_Gregory_VII_-_pilot_project/12781049) (with Charles West and George Litchfield)

# 2019

[Animated Itinerary of King John,](https://sites.google.com/d/1nQb4g6jqk7M0gwaD4Bvw7QKtBg0nkQRV/p/120fMmXEkjhEwEnsgf8fx5v1XKQrf3MdZ/edit)  [Mapping The Itinerary of King Edward I](https://figshare.com/articles/dataset/Mapping_The_Itinerary_of_King_Edward_I/8948699), [Mapping Papal Letters](https://tomstafford.github.io/PapalCorrespondence/) (with Charles West)

# 2018

2018: [@ChoiceEngine - an interactive essay about the psychology of free will](https://github.com/tomstafford/choice-engine-text)

@@

2012: [The Cognitive Science Safari](https://sites.google.com/d/1nQb4g6jqk7M0gwaD4Bvw7QKtBg0nkQRV/p/1Q0M0b1kRUveC9w0Li7Je0A1f1E8PzzYB/edit) was a street-tour of classic social psychology experiments, in Berlin as part of the BMW Guggenheim Lab.

2011: [The Tea Taste Test](https://sites.google.com/d/1nQb4g6jqk7M0gwaD4Bvw7QKtBg0nkQRV/p/1O7uZnZPiKBL7C6JiR0DLSgGCqVw86uYX/edit) -- explaining why statistics are important to psychology, using a controversy of how to make a cup of tea.

### 2024-05-12 papers.qmd
update

---
title: "Publications"
---

@@

[Back to top](https://tomstafford.sites.sheffield.ac.uk/outputs/conference-papers)

@@

>>>>

---
title: "Papers"
---

@@

@@

# Books and chapters

-   Stafford, T. (2011). [How do we use computational models of cognitive processes?](https://drive.google.com/file/d/1aXmvysI3PVNXGEdsMpAXunptvwUuez6h/view?usp=sharing) (PDF, 289KB) In E. Davelaar (eds) Connectionist Models Of Neurocognition And Emergent Behavior: Proceedings of the 12th Neural Computation and Psychology Workshop, 326--342. World Scientific.

-   Stafford, T. (2010).[ The Narrative Escape](http://mindhacks.com/2010/10/21/the-narrative-escape/), 40kbooks, Milan.

-   Moore, G & Stafford, T. (2010). [The Rough Guide Book of Brain Training](http://idiolect.org.uk/braintrain/).

-   Stafford, T. (2009) Hacking our tools for thought in Nold, C. (ed) Emotional Cartography: Technologies of the Self, 88-96. [emotionalcartography.net](http://emotionalcartography.net/)

-   Stafford, T. (2009). [What use are computational models of cognitive processes?](https://drive.google.com/file/d/19ZS4cAaAIlHcC0kTqOtJHAfox-4GRQlB/view?usp=sharing) (PDF, 132KB) In J. Mayor, N. Ruh and K. Plunkett (eds.) Connectionist Models of Behavior and Cognition II: Proceedings of the 11th Neural Computation and Psychology Workshop, 265--274. World Scientific.

-   Catney, P., Eiser, J.R., Henneberry, J. and Stafford, T. (2007) Democracy, Trust and Risk Related to Contaminated Sites in the UK, in: T. Dixon, M. Raco, P. Catney & D.N. Lerner (Eds.) Sustainable Brownfield Regeneration: Liveable Places from Problem Spaces. Oxford: Blackwells.

-   Stafford, T. and Gurney, K.N. (2006). Computational Models of Cognition. In An Introduction to Cognitive Psychology: Processes and Disorders. Second Edition. Ed. David Groome. Hove, UK: Psychology Press.

Stafford, T. and Webb, M. (2004). [Mind Hacks: Tips and Tricks for using your brain](http://www.mindhacks.com/). Sebastapol, CA: O'Reilly.
